---
title: "mareg"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

[mareg](https://github.com/BigelowLab/mareg) is a small alternative to the much more
robust and "live" [mregions](https://CRAN.R-project.org/package=mregions) R package. 

`mareg` simplifies access to **locally stored** data from [Marine Regions](marineregions.org). Unlike `mregions`, `mareg` does not fetch data for the user.  Instead, the user downloads the 
desired data and stores in a directory. 

### Requirements

  + [R v 4.1+](hlo1ttps://www.r-project.org/)
  
  + [sf](https://CRAN.R-project.org/package=sf)
  
  + [rappdirs](https://CRAN.R-project.org/package=rappdirs)

### Installation

```
remotes::install_github("BigelowLab/mareg")
```

### The data path

Where the data directory resides is up to the user (mine is in `~/Dropbox/data/marineregions`).  The user then creates a hidden text file, named `~/.marineregions` in the users home directory.  The `mareg` package reads that file automatically.

### Download data

Visit [Marine Regions](https://www.marineregions.org/downloads.php) download portal to downlaod the data you desire.  I choose [geopackage](https://www.geopackage.org/) format - it plays well with [sf](https://CRAN.R-project.org/package=sf), but other options are available. 

Move the downloaded data into the data directory you established.  If you download a zipped file, be sure to unpack it.  If what gets unpacked is a directory, move the entire directory into the data directory.

### Listing data

First check that the package is mining the hidden path descriptor file correctly.

```{r}
library(mareg)
mareg_root()
```

Now list the contents (this will vary based upon what you have downloaded...)

```{r}
list_mareg()
```

Hmmm.  Let's list what is inside.

```{r}
list_mareg(recursive = TRUE)
```

### Reading EEZ v11

We have an interest in EEZ v11, so we wrote a function for that.  Fist we read in the default low resolution.

```{r}
lo <- read_eez() |>
  dplyr::glimpse()
```

And compare that to the high resolution.
```{r}
hi <- read_eez(res = "high") |>
  dplyr::glimpse()
```